### 2018-04-28 paper/algorithm.tex
Removes no-longer-needed comment
Updates some comments

\commentDaniel{%
  We must cover how to do \(\Pr[d \text{ offline at time } t]\) as used in 
  \cref{ExtendRoute}.
  This is probably part of getting random peers in the same place.%
}

\commentDaniel{%
  What is the probability distribution of the peer sample that we get?
  Will it be close to uniformly random?%
}

@@

\commentDaniel{%
  We must do the scheduling: \ie divide the file \(f\) into \(f_1, \dotsc, f_n\) 
  and how the size of \(f_i\) relates to transmission time and size of the 
  timeslot (for the validity of predictions).
  After that we just do \(\SPOR[\Send]\) on each \(f_i\).%
}

>>>>

\commentDaniel{%
  We must cover above how to compute \(p_d\) below, \ie the probability of being 
  online.
  We need this for \cref{ExtendRoute}.%
}

\commentDaniel{%
  What is the probability distribution of the peer sample that we get?
  Will it be close to uniformly random?
  I need this for the security analysis.%
}

@@
